The development of infants' responses to mispronunciations - A Meta-Analysis

### 2019-01-10 Paper_Analyses.tex
added references, organized old files

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words {[}Primir, Kuhl, Best{]}. In a mature phono-lexical
system, word recognition must balance flexibility to slight variation
(e.g., speaker identity, accented speech) while distinguishing between
phonetic details that differentiate words in their native language
(e.g.~cat-hat). To build robust language knowledge, it seems ueful to
acquire this ability early during development. Indeed, before children
can correctly pronounce a word, they already are aware that slight
phonological deviations might signal a change in word meaning {[}Clark
\& Clark, 1977{]}. This mispronunciation sensitivity reflects the
specificity with which infants represent the phonological information of
familiar words. As infants continue to develop into expert language
users, their language processing matures and becomes more efficient,
including their knowledge of what consistutes a permissible versus
word-changing phonological deviation. In this paper, we aggregate and
analyze the almost 20 years of literature investigating mispronunciation
sensitivity in infants in an attempt to uncover its characteristics and
the trajectory of its development.

At the turn of the millenia, infant language acquisition researchers had
established that during their first years of life, infants are sensitive
to changes in the phonetic detail of newly segmented words (Jusczyk \&
Aslin, 1995) and learned minimal pairs (Stager \& Werker, 1997).
Furthermore, when presented with familiar image pairs, children fixate
on one image upon hearing its label (Fernald, Pinto, Swingley, Weinberg,
\& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and Aslin (2000)
were the first to tie these lines of research together and investigate
mispronunciation sensitivity in infant familiar word recognition:
Children aged 18 to 23 months learning American English saw pairs of
images (e.g.~a baby and a dog) and their eye movements to each image
were recorded and subsequently coded offline. On \enquote{correct}
trials, children heard the correct label for one of the images (e.g.
\enquote{baby}). On \enquote{mispronounced} trials, children heard a
mispronounced label of one of the images (e.g. \enquote{vaby}). The mean
proportion of fixations to the target image (here: a baby) was
calculated separately for both correct and mispronounced trials by
dividing the target looking time by the sum of total looking time to
both target and a distractor (proportion of target looking or PTL). Mean
fixations in correct trials were significantly greater than in
mispronounced trials, and in both conditions looks to the target were
significantly greater than chance. We refer to this pattern of a
difference between looks to correct and mispronounced words as
\emph{mispronunciation sensitivity} and of looks to the target image
above chance in each condition as \emph{object identification}. Swingley
and Aslin (2000) concluded that already before the second birthday,
children represent words with sufficient detail to be sensitive to
mispronunciations.

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
principles that infants must discover in early phonological development
in order to form adult-like word representations: \emph{phonological
constancy} and \emph{phonological distinctiveness}. Phonological
constancy is the ability to resolve phonological variation across
different instances of a word, as long as the variation does not
compromise the overall identity of the word. For example, different
speakers - particularly across genders and accents - produce the same
word with notable acoustic variation, although the word remains the
same. In contrast, phonological distinctiveness describes the ability to
differentiate between different words that happen to be phonologically
similar, such as bad/bed or cat/hat. To successfully recognize words,
speakers of a given language must therefore simultaneously use both
phonological constancy and distinctiveness to determine where
phonological variation is appropriate and where it changes a word's
meaning. Both abilities have to be acquired, because language systems
differ in which sounds signal a meaning change.

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological distinctiveness and
constancy by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively supported by single
studies and two predicted by theoretical accounts. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants than is possible in most single studies (see Frank et
al., 2018; for a notable exception). Before we outline the
meta-analytical approach and its advantages in detail, we first discuss
the proposals this study seeks to disentangle and the data supporting
each of the accounts.

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months, and is
therefore related to vocabulary growth. In this case, we would expect
the size of mispronunciation sensitivity to be larger at younger ages
and \emph{decrease} as the child matures and learn more words, although
children continue to detect mispronunciations. Indeed, young infants are
more perturbed by accented speakers than older infants in their
recognition of familiar words (Best, Tyler, Gooding, Orlando, \& Quann,
2009; Mulak, Best, \& Tyler, 2013) or learning of new words (Schmale,
Hollich, \& Seidl, 2011).

According to a different theoretical framework, young infants may
instead begin with phonologically broad representations for familiar
words and only refine their representations as language experience
accumulates. PRIMIR (Processing Rich Information from Multidimensional
Interactive Representations; Curtin \& Werker, 2007; Werker \& Curtin,
2005; Curtin, Byers-Heinlein, \& Werker, 2011) describes the development
of phonemic categories emerging as the number of word form-meaning
linkages increases. Vocabulary growth, therefore, promotes more detailed
phonological representations in familiar words. Following this account,
we predict an \emph{increase} in mispronunciation sensitivity as infants
mature and add more words to their growing lexicon.

@@

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 9 months
(Bergelson \& Swingley, 2017), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only a handful of studies have compared more than one age group
on the same mispronunciation task (see Table X), making the current
meta-analysis very informative. One study has found evidence for infants
to become \emph{less} sensitive to mispronunciations as children
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of features changed (see below
for a discussion of the role of features). 18-month-olds were sensitive
to mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

In contrast, other studies have found evidence for \emph{greater}
mispronunciation sensitivity as children develop. More precisely, the
difference in target looking for correct and mispronounced trials is
smaller in younger infants and grows as infants develop. Mani and
Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
English; although all three groups were sensitive to mispronunciations,
15-month-olds showed a less robust sensitivity. An increase in
sensitivity to mispronunciations has also been found from 20 to 24
months (van der Feest \& Fikkert, 2015) and 15 to 18 months (Altvater
Mackensen et al., 2013) in Dutch infants, as well as German infants from
22 to 25 months (Altvater-Mackensen, 2010). Furthermore, van der Feest
and Fikkert (2015) found that sensitivity to specific kinds of
mispronunciations develop at different ages depending on language
infants are learning. In other words, the native language constraints
which \emph{kinds} of mispronunciations infants are sensitive to first,
and that as infants develop, they become sensitive to other
mispronunciations. These studies award support to the prediction that
mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation
sensitivity) did not. This suggests that as children develop, they are
more likely to look at the target in the presence of a mispronounced
label and that age is not related to mispronunciation sensitivity. A
similar response pattern has been found for British English learning
infants aged between 18 and 24 months (Bailey \& Plunkett, 2002) as well
as younger French-learning infants at 12 and 17 months (Zesiger,
Lozeron, Levy, \& Frauenfelder, 2012). These studies award support to
the prediction that mispronunciation sensitivity does not change with
development.

Why would mispronunciation sensitivity change as infants develop, and
would it increase or decrease? The main hypothesis is related to
vocabulary growth. Both the Perceptual Attunement (Best, 1994; 1995) and
PRIMIR (Curtin \& Werker, 2007; Werker \& Curtin, 2005; Curtin,
Byers-Heinlein, \& Werker, 2011) accounts situate a change in
mispronunciation sensitivity occurring along with an increase in
vocabulary size, particularly with the vocabulary spurt at about 18
months. Knowing more words helps infants shift their focus to the
relevant phonetic dimensions needed for word recognition. On the one
hand, a smaller lexicon does not require full specification to
differentiate between words; as more phonologically similar words are
learned, so does the need to have fully detailed representations for
those words (Charles-Luce \& Luce, 1995). On the other hand, a growing
vocabulary is also related to more experience or familiarity with words,
which may sharpen the detail of their representation (Barton, 1980).

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Swingley \& Aslin 2000; 2002; Bailey \&
Plunkett, 2002; Zesiger, Lozeron, Levy, \& Frauenfelder, 2012; Swingley,
2009; Ballem \& Plunkett, 2005; Mani \& Plunkett, 2007; Mani, Coleman,
\& Plunkett, 2008). One notable exception comes from Mani and Plunkett
(2010: keps and tups). Here, 12-month-old infants were divided into a
low and high vocabulary group based on median vocabulary size. High
vocabulary infants showed greater sensitivity to vowel mispronunciations
than low vocabulary infants, although this was not the case for
consonant mispronunciations. Taken together, although receiving
considerable support from theories of phono-lexical processing in
language acquisition, there is very little evidence for a role of
vocabulary size in mispronunciation sensitivity. In our current
meta-analysis, we include the relationship between mispronunciation
sensitivity and vocabulary size to further disentangle the disconnect
between theory and experimental results.

In sum, the studies we have reviewed begin to paint a picture of the
development of mispronunciation sensitivity. Each study contributes one
separate brushstroke and it is only by examining all of them together
that we can achieve a better understanding of early language
development. Meta-analyses can provide thus further insights by
estimating the population effect, both of infants' responses to correct
and mispronounced labels, and their mispronunciations sensitivity.
Because we aggregate data over various age groups, this meta-analysis
can also investigate the role of maturation by assessing the impact of
age and vocabulary size. As a consequence, our results will be important
in evaluating theories and drive future research. We also make hands-on
recommendations for experiment planning, for example by providing an
effect size estimate for a priori power analyses (Bergmann et al.,
2018).

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab (metalab.stanford.edu; Bergmann et al.,
2018). Since the present paper was written with embedded analysis
scripts in R {[}@R, @RMarkdown, @papaja{]}, it is always possible to
re-analyze an updated dataset. In addition, we followed the Preferred
Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA)
guidelines and make the corresponding information available as
supplementary materials (Moher, Liberati, Tetzlaff, Altman \&
PRISMAGroup, 2009). Figure 1 plots our PRISMA flowchart illustrating the
paper selection procedure.

@@

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley \& Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{34}) consisted of 28
journal articles, 1 proceedings paper, 3 thesis, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Tsuji, Bergmann, \& Cristia,
2014; Bergmann et al., 2018). For each experiment (note that a paper
typically has multiple experiments), we entered variables describing the
publication, population, experiment design and stimuli, and results. For
the planned analyses to evaluate the development of mispronunciation
sensitivity, we focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

@@

Effect sizes are reported for infants' looks to target pictures after
hearing a correctly pronounced or a mispronounced label (object
identification) as well as the difference between effect sizes for
correct and mispronounced trials (i.e.~mispronunciation sensitivity).
The effect size reported in the present paper is based on comparison of
means, standardized by their variance. The most well-known effect size
from this group is Cohen's \emph{d} {[}@cohen{]}. To correct for the
small sample sizes common in infant research, however, we used as a
dependent variable Hedges' \emph{g} instead of Cohen's \emph{d} (Hedges,
1981; Morris, 2000).

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or using reported t-values (\emph{n} = 74 records from 9 papers). Two
papers reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Swingley, 2016; Altvater-Mackensen et al., 2014). Raw means and
standard deviations were extracted from figures for 4 papers. In a
within-participation design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance based on t-values. Upon request we
were provided with correlation values for one paper (Altvater-Mackensen,
2010); we were able to compute correlations using means, standard
deviations, and t-values for \emph{n} = 5 (following Csibra, et al.
2016, Appendix B; see also Rabagliati, Ferguson, \& Lew-Williams, 2018).
Correlations were imputed for the remaining papers (see Black \&
Bergmann, 2017, for the same procedure). For two papers, we could not
derive any effect size (Ballem \& Plunkett, Renner), and for a third
paper, we do not have sufficient information in one record to compute
effect sizes (Skoruppa). We compute a total of 106 effect sizes for
correct pronunciations and 150 for mispronunciations. Following standard
meta-analytic practice, we remove outliers, i.e.~effect sizes more than
3 standard deviations from the respective mean effect size. This leads
to the exclusion of 2 records for correct pronunciations and 3 records
for mispronunciations.

To take into account the fact that the same infants contributed to
multiple datapoints, we analyze our results in a multilevel approach
using the R {[}@R{]} package metafor {[}@metafor{]}. This means we model
as random effect that effect sizes from the same paper share are based
on more similar studies than those across papers and that nested therein
effects can stem from the same infants.

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to some baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; we used
the baseline reported by the authors of each paper. Most papers
(\emph{n} = 52 records from 13 papers) subtracted the PTL score for a
pre-naming baseline phase from the PTL score for a post-naming phase and
report a difference score.

@@

In the psychological sciences, there is a documented reluctance to
publish null results. As a result, significant results tend to be
over-reported and thus might be over-represented in our meta-analyses
(see Ferguson \& Heene, 2012). To examine whether this is also the case
in the mispronunciation sensitivity literature, which would bias the
data analyzed in this meta-analysis, we conducted two tests. We first
examined whether effect sizes are distributed as expected based on
sampling error using the rank correlation test of funnel plot asymmetry
with the R {[}@R{]} package metafor {[}@metafor{]}. Effect sizes with
low variance were expected to fall closer to the estimated mean, while
effect sizes with high variance should show an increased,
evenly-distributed spread around the estimated mean. Publication bias
would lead to an uneven spread.

>>>>

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words (Best, 1994, 1995; Curtin \& Werker, 2007; Kuhl, 2004;
Werker \& Curtin, 2005). In a mature phono-lexical system, word
recognition must balance flexibility to slight variation (e.g., speaker
identity, accented speech) while distinguishing between phonetic details
that differentiate words in a given language (e.g.~cat-hat). To build
robust language knowledge, it seems ueful to acquire this ability early
during development. Indeed, before children can correctly pronounce a
word, they already are aware that slight phonological deviations might
signal a change in word meaning (H. H. Clark \& Clark, 1977). This
mispronunciation sensitivity reflects the specificity with which infants
represent the phonological information of familiar words. As infants
continue to develop into expert language users, their language
processing matures and becomes more efficient, including their knowledge
of what consistutes a permissible versus word-changing phonological
deviation. In this paper, we aggregate and analyze the nearly 20 years
of literature investigating mispronunciation sensitivity in infants in
an attempt to uncover its characteristics and the trajectory of its
development.

At the turn of the millenium, infant language acquisition researchers
had established that during their first years of life, infants are
sensitive to changes in the phonetic detail of newly segmented words
(Jusczyk \& Aslin, 1995) and learned minimal pairs (Stager \& Werker,
1997). Furthermore, when presented with familiar image pairs, children
fixate on the referent of a spoken label (Fernald, Pinto, Swingley,
Weinberg, \& McRoberts, 1998; Tincoff \& Jusczyk, 1999). Swingley and
Aslin (2000) were the first to tie these lines of research together and
investigate mispronunciation sensitivity in infant familiar word
recognition: Children aged 18 to 23 months learning American English saw
pairs of images (e.g.~a baby and a dog) and their eye movements to each
image were recorded and subsequently coded offline. On \enquote{correct}
trials, children heard the correct label for one of the images (e.g.
\enquote{baby}). On \enquote{mispronounced} trials, children heard a
mispronounced label of one of the images (e.g. \enquote{vaby}). The mean
proportion of fixations to the target image (here: a baby) was
calculated separately for both correct and mispronounced trials by
dividing the target looking time by the sum of total looking time to
both target and a distractor (proportion of target looking or PTL). Mean
fixations in correct trials were significantly greater than in
mispronounced trials, and in both conditions looks to the target were
significantly greater than chance. We refer to this pattern of a
difference between looks to correct and mispronounced words as
\emph{mispronunciation sensitivity} and of looks to the target image
above chance in each condition as \emph{object identification}. Swingley
and Aslin (2000) concluded that already before the second birthday,
children represent words with sufficient detail to be sensitive to
mispronunciations.

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
principles that infants must discover in early phonological development
in order to form adult-like word representations and processing
capabilities: \emph{phonological constancy} and \emph{phonological
distinctiveness}. Phonological constancy is the ability to resolve
phonological variation across different instances of a word, as long as
the variation does not compromise the overall identity of the word. For
example, different speakers - particularly across genders and accents -
produce the same word with notable acoustic variation, although the word
remains the same. In contrast, phonological distinctiveness describes
the ability to differentiate between different words that happen to be
phonologically similar, such as bad/bed or cat/hat. To successfully
recognize words, speakers of a given language must therefore
simultaneously use both phonological constancy and distinctiveness to
determine where phonological variation is appropriate and where it
changes a word's meaning. Both abilities have to be acquired, because
language systems differ in which sounds signal a meaning change.

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological distinctiveness and
constancy by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively supported by single
studies and additionally two possibilities are predicted by key
theoretical accounts. By aggregating all publicly available evidence
using meta-analysis, we can examine developmental trends making use of
data from a much larger and diverse sample of infants than is possible
in most single studies (see Frank et al., 2018; for a notable
exception). Before we outline the meta-analytical approach and its
advantages in detail, we first discuss the proposals this study seeks to
disentangle and the data supporting each of the accounts.

{[}Katie: Christina, do you know which citation the Frank et al., 2018
citation is referring to above? He's published a gazilion papers in
2018{]}

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best, 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months,
because it is causally related to vocabulary growth. In this case, we
would expect the size of mispronunciation sensitivity to be larger at
younger ages and \emph{decrease} as the child matures and learn more
words, although children continue to detect mispronunciations. Indeed,
young infants are more perturbed by accented speakers than older infants
in their recognition of familiar words (Best, Tyler, Gooding, Orlando,
\& Quann, 2009; Mulak, Best, Tyler, Kitamura, \& Irwin, 2014) or
learning of new words (Schmale, Hollich, \& Seidl, 2011).

According to a different theoretical framework, young infants may
instead begin with phonologically broad representations for familiar
words and only refine their representations as language experience
accumulates. PRIMIR ((Processing Rich Information from Multidimensional
Interactive Representations; Curtin \& Werker, 2007; Curtin,
Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005)) describes the
development of phonemic categories emerging as the number of word
form-meaning linkages increases. Vocabulary growth, therefore, promotes
more detailed phonological representations in familiar words. Following
this account, we predict an \emph{increase} in mispronunciation
sensitivity as infants mature and add more words to their growing
lexicon.

@@

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 9 months
(Bergelson \& Swingley, 2017), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only about half of studies have compared more than one age
group on the same mispronunciation task (see Table 1), making the
current meta-analysis very informative. One study has found evidence for
infants to become \emph{less} sensitive to mispronunciations as they
develop. Mani and Plunkett (2011) presented 18- and 24-month-olds with
mispronunciations varying in the number of phonological features changed
(e.g., changing an p into a b, a 1-feature change, versus changing a p
into a g, a 2-feature change). 18-month-olds were sensitive to
mispronunciations, regardless of the number of features changed.
24-month-olds, in contrast, fixated the target image equally for both
correct and 1-feature mispronounced trials, although they were sensitive
to larger mispronunciations. In other words, for 1-feature
mispronunciations at least, sensitivity decreased from 18 to 24 months,
providing support to the prediction that mispronunciation sensitivity
may decrease with development.

In contrast, other studies have found evidence for \emph{greater}
mispronunciation sensitivity as children develop. More precisely, the
difference in target looking for correct and mispronounced trials is
reported to be smaller in younger infants and grows as infants develop.
Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning
British English; although all three groups were sensitive to
mispronunciations, 15-month-olds showed a less robust sensitivity. An
increase in sensitivity to mispronunciations has also been found from 20
to 24 months (Feest \& Fikkert, 2015) and 15 to 18 months
(Altvater-Mackensen, Feest, \& Fikkert, 2014) in Dutch infants, as well
as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
Furthermore, Feest and Fikkert (2015) found that sensitivity to specific
kinds of mispronunciations develop at different ages depending on
language infants are learning. In other words, the native language
constraints which \emph{kinds} of mispronunciations infants are
sensitive to first, and that as infants develop, they become sensitive
to other mispronunciations. These studies award support to the
prediction that mispronunciation sensitivity improves with development.

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation
sensitivity) did not. This suggests that as children develop, they are
more likely to look at the target in the presence of a correct or
mispronounced label, but that the difference between the two does not
change. A similar response pattern has been found for British English
learning infants aged between 18 and 24 months (Bailey \& Plunkett,
2002) as well as younger French-learning infants at 12 and 17 months
(Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These studies award
support to the prediction that mispronunciation sensitivity does not
change with development.

Why would mispronunciation sensitivity change as infants develop, and
would it increase or decrease? The main hypotheses attribute change to
vocabulary growth. Both the Perceptual Attunement (Best, 1994, 1995) and
PRIMIR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
2005) accounts situate a change in mispronunciation sensitivity
occurring along with an increase in vocabulary size, particularly with
the vocabulary spurt at about 18 months. As infants learn more words,
their focus shifts to the relevant phonetic dimensions needed for word
recognition. For example, an infant who knows a handful of words with
few phonological neighbors would not need to have fully specified
phonological representations in order to differentiate between these
words. As more phonologically similar words are learned, however, the
need for fully detailed phonological representations increases
(Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also
reflects increased experience or familiarity with words, which may
sharpen the detail of their phonological representation (Barton, Miller,
\& Macken, 1980). If vocabulary growth leads to an increase in the
phonological specificity of infants' word representation, we should find
a relationship between vocabulary size and mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett,
2005; Mani \& Plunkett, 2007; Mani, Coleman, \& Plunkett, 2008;
Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012).
One notable exception comes from Mani and Plunkett (2010). Here,
12-month-old infants were divided into a low and high vocabulary group
based on median vocabulary size. High vocabulary infants showed greater
sensitivity to vowel mispronunciations than low vocabulary infants,
although this was not the case for consonant mispronunciations. Taken
together, although receiving considerable support from theories of
phono-lexical processing in language acquisition, there is very little
evidence for a role of vocabulary size in mispronunciation sensitivity.
In our current meta-analysis, we include the relationship between
mispronunciation sensitivity and vocabulary size to further disentangle
the disconnect between theory and experimental results.

In sum, the studies we have reviewed begin to paint a picture of the
development of mispronunciation sensitivity. Each study contributes one
separate brushstroke and it is only by examining all of them together
that we can achieve a better understanding of the big picture of early
language development. Meta-analyses can provide unique insights by
estimating the population effect, both of infants' responses to correct
and mispronounced labels, and their mispronunciations sensitivity.
Because we aggregate data over various age groups, this meta-analysis
can also investigate the role of maturation by assessing the impact of
age and vocabulary size. As a consequence, our results will be important
in evaluating theories and drive future research. We also make hands-on
recommendations for experiment planning, for example by providing an
effect size estimate for a priori power analyses (Bergmann et al.,
2018).

@@

The present meta-analysis was conducted with maximal transparency and
reproducibility in mind. To this end, we provide all data and analysis
scripts on the supplementary website (\url{https://osf.io/rvbjs/}) and
open our meta-analysis up for updates (Tsuji, Bergmann, \& Cristia,
2014). The most recent version is available via the website and the
interactive platform MetaLab ((\url{https://metalab.stanford.edu};
Bergmann et al., 2018)). Since the present paper was written with
embedded analysis scripts in R (R Core Team, 2018, Allaire et al.
(2018), Aust and Barth (2018)), it is always possible to re-analyze an
updated dataset. In addition, we followed the Preferred Reporting Items
for Systematic Reviews and Meta-Analyses (PRISMA) guidelines and make
the corresponding information available as supplementary materials
(Moher, Liberati, Tetzlaff, Altman, \& Group, 2009). Figure 1 plots our
PRISMA flowchart illustrating the paper selection procedure.

@@

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley and Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{34}) consisted of 28
journal articles, 1 proceedings paper, 3 theses, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Bergmann et al., 2018; Tsuji
et al., 2014). For each experiment (note that a paper typically has
multiple experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the planned
analyses to evaluate the development of mispronunciation sensitivity, we
focus on the following characteristics:

@@

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row ((e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007)). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

@@

Effect sizes are reported for infants' looks to target pictures after
hearing a correctly pronounced or a mispronounced label (object
identification) as well as the difference between effect sizes for
correct and mispronounced trials (i.e.~mispronunciation sensitivity).
The effect size reported in the present paper is based on comparison of
means, standardized by their variance. The most well-known effect size
from this group is Cohen's \emph{d} (Cohen, 1988). To correct for the
small sample sizes common in infant research, however, we used Hedges'
\emph{g} instead of Cohen's \emph{d} (Hedges, 1981; Morris \& DeShon,
2002).

We calculated Hedges' \emph{g} using the raw means and standard
deviations reported in the paper (\emph{n} = 186 records from 26 papers)
or reported t-values (\emph{n} = 74 records from 9 papers). Two papers
reported raw means and standard deviations for some experimental
conditions and just t-values for the remaining experimental conditions
(Altvater-Mackensen et al., 2014; Swingley, 2016). Raw means and
standard deviations were extracted from figures for 4 papers. In a
within-participant design, when two means are compared (i.e.~looking
during pre- and post-naming) it is necessary to obtain correlations
between the two measurements at the participant level to calculate
effect sizes and effect size variance. Upon request we were provided
with correlation values for one paper (Altvater-Mackensen, 2010); we
were able to compute correlations using means, standard deviations, and
t-values for 5 papers ((following Csibra, Hernik, Mascaro, Tatone, \&
Lengyel, 2016; see also Rabagliati, Ferguson, \& Lew-Williams, 2018)).
Correlations were imputed for the remaining papers ((see Black \&
Bergmann, 2017 for the same procedure)). For two papers, we could not
derive any effect size (Ballem \& Plunkett, 2005; Renner, 2017), and for
a third paper, we do not have sufficient information in one record to
compute effect sizes (Skoruppa, Mani, Plunkett, Cabrol, \& Peperkamp,
2013). We compute a total of 106 effect sizes for correct pronunciations
and 150 for mispronunciations. Following standard meta-analytic
practice, we remove outliers, i.e.~effect sizes more than 3 standard
deviations from the respective mean effect size. This leads to the
exclusion of 2 records for correct pronunciations and 3 records for
mispronunciations.

{[}Katie: Mention of Renner here{]}

To take into account the fact that the same infants contributed to
multiple datapoints, we analyze our results in a multilevel approach
using the R (R Core Team, 2018) package metafor (Viechtbauer, 2010). We
use a multilevel random effects model which estimates the mean and
variance of effect sizes sampled from an assumed distribution of effect
sizes. In the random effect structure we take into account the shared
variance of effect sizes drawn from the same paper, and nested therein
that the same infants might contribute to multiple effect sizes.

Mispronunciation sensitivity studies typically examine infants'
proportion of target looks (PTL) in comparison to some baseline
measurement. PTL is calculated by dividing the percentage of looks to
the target by the total percentage of looks to both the target and
distractor images. Across papers the baseline comparison varied; since
other options were not available to us, we used the baseline reported by
the authors of each paper. Most papers (\emph{n} = 52 records from 13
papers) subtracted the PTL score for a pre-naming baseline phase from
the PTL score for a post-naming phase and report a difference score.

@@

In the psychological sciences, there is a documented reluctance to
publish null results. As a result, significant results tend to be
over-reported and thus might be over-represented in our meta-analyses
((see C. J. Ferguson \& Heene, 2012)). To examine whether this is also
the case in the mispronunciation sensitivity literature, which would
bias the data analyzed in this meta-analysis, we conducted two tests. We
first examined whether effect sizes are distributed as expected based on
sampling error using the rank correlation test of funnel plot asymmetry
with the R (R Core Team, 2018) package metafor (Viechtbauer, 2010).
Effect sizes with low variance were expected to fall closer to the
estimated mean, while effect sizes with high variance should show an
increased, evenly-distributed spread around the estimated mean.
Publication bias would lead to an uneven spread.

Second, we analyze all of the significant results in the dataset using a
p-curve from the p-curve app ((v4.0, \url{http://p-curve.com};
Simonsohn, Nelson, \& Simmons, 2014)). This p-curve tests for evidential
value by examining whether the p-values follow the expected distribution
of a right skew in case the alternative hypothesis is true, versus a
flat distribution that speaks for no effect being present in the
population and all observed significant effects being spurious.

Responses to correctly pronounced and mispronounced labels were
predicted to show different patterns of looking behavior. In other
words, there is an expectation that infants should look to the target
when hearing a correct pronunciation, but studies vary in their report
of significant looks to the target when hearing a mispronounced label
(i.e.~there might be no effect present in the population); as a result,
we conducted these two analyses to assess publication bias separately
for both conditions.
